Forecasting short-term hourly Emergency Department arrivals

### 2022-01-12 paper/paper.tex
add page title and correct typos

Figure \ref{fig:hourly-plot-ridge} highlights the week of year seasonality in the ED arrivals. We observe that arrivals are significantly lower from week 29 to 35, which corresponds to the summer period. Moreover, the number of arrivals are lower at beginning and the end of the year. The highest arrivals are in week 39-42.

@@

Figure \ref{fig:hourly-plot-ridge} presents the time plot of daily arrivals. Each point represents one day, and points are shape-coded by day-of-week to show the weekly cycle. The figure shows more arrivals on Mondays compared to other weekdays. Moreover, we can observe a long-term trend line as well as the significant effect of some holidays. We can see that arrivals near Christmas and New Year's day are significantly lower than other days of the year. Moreover, Figure \ref{fig:hourly-plot-ridge} allows us to identify the impact of special event on arrivals. For instance, we see that the number of arrivals are significamtly low for 01-03 of March 2018. These days correspond to the Storm Emma with heavy snowfall that resulted in travel disruption, mass power outages and schools closed in the UK \citep{stormemma2018}.

>>>>

Figure \ref{fig:seasonplot-weekofyear} highlights the week of year seasonality in the ED arrivals. We observe that arrivals are significantly lower from week 29 to 35, which corresponds to the summer period. Moreover, the number of arrivals are lower at beginning and the end of the year. The highest arrivals are in week 39-42.

@@

Figure \ref{fig:date-plot} presents the time plot of daily arrivals. Each point represents one day, and points are shape-coded by day-of-week to show the weekly cycle. The figure shows more arrivals on Mondays compared to other weekdays. Moreover, we can observe a long-term trend line as well as the significant effect of some holidays. We can see that arrivals near Christmas and New Year's day are significantly lower than other days of the year. Moreover, Figure \ref{fig:date-plot} allows us to identify the impact of special event on arrivals. For instance, we see that the number of arrivals are significantly low for 01-03 of March 2018. These days correspond to the Storm Emma with heavy snowfall that resulted in travel disruption, mass power outages and schools closed in the UK \citep{stormemma2018}.
